Approximation as Differentiation

### 2025-06-09 main/first-order.tex
Clarify CMon monoidal.

For differentiable functions, we can combine linear approximations by adding tangent vectors. For stable
functions, we can combine approximants by taking their meet. The additive structure in both cases form a
commutative monoid with an addition + and zero element 0. A category $\cat{C}$ is enriched in $\CMon$ (or a
$\CMon$-category), the category of commutative monoids, if every hom-set $\cat{C}(X,Y)$ has a similar additive
structure, providing an operation + to add morphisms together plus a zero morphism $0: X \to Y$, and if
composition is \emph{bilinear}, i.e.~given by a family of morphisms $\Hom{\cat{C}}{Y}{Z} \tensor
\Hom{\cat{C}}{X}{Y} \to \Hom{\cat{C}}{X}{Z}$ in $\CMon$ that preserve the additive structure in
$\Hom{\cat{C}}{Y}{Z}$ and $\Hom{\cat{C}}{X}{Y}$ separately:

>>>>

For differentiable functions, we can combine linear approximations by adding tangent vectors. For stable
functions, we can combine approximants by taking their meet. The additive structure in both cases form a
commutative monoid with an addition + and zero element 0. A category $\cat{C}$ is enriched in $\CMon$, the
(monoidal) category of commutative monoids, when every hom-set $\cat{C}(X,Y)$ has a similar additive
structure, providing an operation + to add morphisms together plus a zero morphism $0: X \to Y$, and
composition is \emph{bilinear}, i.e.~given by a family of morphisms $\Hom{\cat{C}}{Y}{Z} \tensor
\Hom{\cat{C}}{X}{Y} \to \Hom{\cat{C}}{X}{Z}$ in $\CMon$ that preserve the additive structure in
$\Hom{\cat{C}}{Y}{Z}$ and $\Hom{\cat{C}}{X}{Y}$ separately:
